Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-10 journal/content.tex
Bigger image
T: External consultants and investments separate subjects

\begin{figure}
  \begin{center}
    \includegraphics{graphics/research_process.pdf}
    \caption{Outline of the research process}
    \label{fig:researchprocess}
  \end{center}
\end{figure}

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        \toprule
        Sources discussing viewpoints on piloting   & 
                P6-P11, P14, P16, P18, P22, P23, P24, P27, P29,
                P36, P38, P40, P41, P43, P45, P46, P47  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of activities aiming to advance the transformation}
    \label{table:transformation_piloting}
\end{table}

@@

Even if any activities aiming for transformation can be considered as
investments in themselves, the transformation process included some specific
tangible investments. These investments were focused on better enabling agile
software development. They also highlight the concerns that organizations had when
implementing an agile model. Typical investments were bringing in external help,
new management tools, improvements in testing environments, and updating of the
physical working spaces. Table \ref{table:transformation_investments} summarizes
common types of investments.

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.35\textwidth}
                     >{\raggedright\arraybackslash}p{0.57\textwidth} }
        \toprule
        Investments during transformation      &  Described in  \\
        \midrule
        Using external consultants  &
                P5-P9, P16-P21, P23 P25, P27, P29-P31,
                P34, P35, P37-P41, P44, P46, P47, P50, P51  \\  % 29
        New project management tools for agile  &
                P10, P11, P14, P16, P17, P26, P33,
                P41, P43, P44, P45, P48, P50 \\
        Creating a continuous build and integration system  &
                P5, P11, P16, P17, P25, P27, P34, P39, P42, P50 \\
        Proprietary agile material or documentation   & 
                P1, P2, P8, P14, P16, P23, P26, P29, P32, P45  \\
        Refurbishing work areas and other spaces   &
                P6, P22, P35, P36, P38, P42, P46, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investments done during transformation, aiming to make
             agile methods perform better}
    \label{table:transformation_investments}
\end{table}

@@

It was very typical that external help was brought in to help with the
transformation.
External consultants were employed especially at the start of the
transformation. At the time it was realized that the way of working should be
changed a consultant was often hired to assess the current state and give a
recommendation on how to proceed [P16, P20, P41, P43, P41, P44, P51].
In the beginning external consultants were used to ignite interest in agile
methods, and provide initial education [P7, P9, P27, P30, P43].
It was recommended to bring in external help as early as possible, when the
internal agile expertise is lacking and before transformation challenges appear
[P6, P16, P30].

@@

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/research_process.pdf}
    \caption{Outline of the research process}
    \label{fig:researchprocess}
  \end{center}
\end{figure}

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        \toprule
        Sources discussing viewpoints on piloting   & 
                P6-P11, P14, P16, P18, P22, P23, P24, P27, P29,
                P36, P38, P40, P41, P43, P45, P46, P47  \\
        \bottomrule
    \end{tabular}
    \caption{Sources discussing viewpoints on piloting}
    \label{table:transformation_piloting}
\end{table}

@@

\subsection{Use of external consultants}

It was very typical that external help was brought in to help with the
transformation.
Primary sources presenting different ways external consultants were employed in
the transformation are listed in table \ref{table:transformation_consultants}.

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        \toprule
        Sources discussing use of external consultants  &
                P5-P9, P16-P21, P23 P25, P27, P29-P31,
                P34, P35, P37-P41, P44, P46, P47, P50, P51  \\  % 29
        \bottomrule
    \end{tabular}
    \caption{Sources discussing use of external consultants}
    \label{table:transformation_consultants}
\end{table}

@@

External consultants were employed especially at the start of the
transformation. At the time it was realized that the way of working should be
changed a consultant was often hired to assess the current state and give a
recommendation on how to proceed [P16, P20, P41, P43, P41, P44, P51].
In the beginning external consultants were used to ignite interest in agile
methods, and provide initial education [P7, P9, P27, P30, P43].
It was recommended to bring in external help as early as possible, when the
internal agile expertise is lacking and before transformation challenges appear
[P6, P16, P30].

@@

Even if any activities aiming for transformation can be considered as
investments in themselves, the transformation process included some specific
tangible investments. These investments were focused on better enabling agile
software development. They also highlight the concerns that organizations had
when implementing an agile model. Typical investments were new management tools,
improvements in testing environments, and updating of the physical working
spaces. Table \ref{table:transformation_investments} summarizes common types of
investments.

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.35\textwidth}
                     >{\raggedright\arraybackslash}p{0.57\textwidth} }
        \toprule
        Investments during transformation      &  Described in  \\
        \midrule
        New project management tools for agile  &
                P10, P11, P14, P16, P17, P26, P33,
                P41, P43, P44, P45, P48, P50 \\
        Creating a continuous build and integration system  &
                P5, P11, P16, P17, P25, P27, P34, P39, P42, P50 \\
        Proprietary agile material or documentation   & 
                P1, P2, P8, P14, P16, P23, P26, P29, P32, P45  \\
        Refurbishing work areas and other spaces   &
                P6, P22, P35, P36, P38, P42, P46, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investments done during transformation, aiming to make
             agile methods perform better}
    \label{table:transformation_investments}
\end{table}
